---
output: md_document
---

```{r include=FALSE}
library(heattree)
fig_width = 850
fig_height = 850
knitr::opts_chunk$set(
  message = FALSE,
  collapse = TRUE,
  fig.width = 10,
  fig.height = 10,
  comment = "#>",
  fig.path = "man/figures/"
  )
```

# The `heattree` R package 

This package makes it easy to visualize, manipulate, and export phylogenetic trees in R using an interactive viewer/editor.
You can insert this tree viewer into Rmd/Quarto documents make your trees accessible online.
If you want to use this for web development outside of R, consider the [javascript `heat-tree` package](https://www.npmjs.com/package/@grunwaldlab/heat-tree) which this package builds upon.


## Installation

For now, `heattree` is only available on Github and can be installed with `devtools`:

```{r eval=FALSE}
devtools::install_github('grunwaldlab/heattree')
```


## Quick start

The package includes example data sets that are automatically loaded with the package (`example_tree_1`), so you can try it out with minimal effort.
After installing the packages, simply run the lines below to get an idea of how it works:

```{r eval=FALSE}
library(heattree)
heat_tree(example_tree_1, metadata = example_metadata_1, aesthetics = c(tipLabelColor = 'source'), layout = 'circular')
```

```{r echo=FALSE}
heat_tree(example_tree_1, metadata = example_metadata_1, aesthetics = c(tipLabelColor = 'source'), layout = 'circular', width = fig_width, height = fig_height)
```


[**See the "Getting Started" page for interactive examples**](articles/Getting-started.html)


## Contributing and feedback

Contributions and feedback are welcome! Please visit the [GitHub repository](https://github.com/grunwaldlab/heattree) to report issues or submit pull requests.
