---
output: github_document
---

```{r include=FALSE}
knitr::opts_chunk$set(
  fig.width = 10,
  fig.height = 10
)
```

# The `heattree` R package 

<!-- badges: start -->
[![R-CMD-check](https://github.com/grunwaldlab/heattree/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/grunwaldlab/heattree/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

This package makes it easy to visualize, manipulate, and export phylogenetic trees in R using an interactive viewer/editor.
You can use this tree viewer in all the same ways other plotting tools are used in R, including in R Markdown or Quarto documents to make your trees accessible online.

For the **full documentation**, including interactive examples and tutorials, see:

[https://grunwaldlab.github.io/heattree/](https://grunwaldlab.github.io/heattree/)

For the **Python** version of this package see:

[https://grunwaldlab.github.io/heattree_py/](https://grunwaldlab.github.io/heattree_py/)

For the **JavaScript** library the is the foundation of this package see:

[https://grunwaldlab.github.io/heat-tree/](https://grunwaldlab.github.io/heat-tree/).

## Installation

For now, `heattree` is only available on Github and can be installed with `devtools`:

```{r eval=FALSE}
devtools::install_github('grunwaldlab/heattree')
```


## Quick start

```{r, child="vignettes/articles/getting_started.Rmd"}
```


## License

MIT


## Contributing and feedback

Contributions and feedback are welcome! Please visit the [GitHub repository](https://github.com/grunwaldlab/heattree) to report issues or submit pull requests.
