---
output: github_document
---

```{r include=FALSE}
knitr::opts_chunk$set(
  fig.width = 10,
  fig.height = 10
)
```

# The `heattree` R package 

<!-- badges: start -->
[![R-CMD-check](https://github.com/grunwaldlab/heattree/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/grunwaldlab/heattree/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

This package makes it easy to visualize, manipulate, and export phylogenetic trees in R using an interactive viewer/editor.
You can insert this tree viewer into Rmd/Quarto documents make your trees accessible online.
If you want to use this for web development outside of R, consider the [javascript `heat-tree` package](https://www.npmjs.com/package/@grunwaldlab/heat-tree) which this package builds upon.


## Installation

For now, `heattree` is only available on Github and can be installed with `devtools`:

```{r eval=FALSE}
devtools::install_github('grunwaldlab/heattree')
```


## Quick start

```{r, child="vignettes/articles/getting_started.Rmd"}
```


## License

MIT


## Contributing and feedback

Contributions and feedback are welcome! Please visit the [GitHub repository](https://github.com/grunwaldlab/heattree) to report issues or submit pull requests.
